\acknowledgment

I would first like to thank my advisor, Prof. Danilo Erricolo, for his assistance and input on this thesis. Without his guidance and expertise, this paper would not be possible. 

I would like to thank my entire thesis committee, Prof. Danilo Erricolo, Prof. Piergiorgio L. E. Uslenghi and Prof. Pai-Yen Chen, for their time and energy in reviewing this thesis, and their support and assistance throughout the process. 

I would next like to thank the University of Illinois at Chicago, specifically the departments of Electrical and Computer Engineering, and Physics, for not only allowing me the opportunity to study at the university with wonderful professors and students, but also for the financial support which made it all possible. 

I would like to thank my current employer, Northrop Grumman, for financially supporting the completion my studies. I would also like to thank many of the people I work with at Northrop Grumman for their flexibility in working with me while completing this thesis, including Mike Davis, Michael Moore, Heather Kang, Curtis Harkrider, Ben Wallace, Jim Atwood, Ron Jones, Mike Kernal, James Kless, Gerardo De La Torre, Jeremy Feldstein and Mike Johnson. 

I would like to thank my parents, Brian and Suzanne, for their love and support throughout the years. They always nurtured my curiosity, despite the dangerous results of my early experiments. 

I would like to thank my siblings, Anne Rose and Michael, for their encouragement. Our perpetual sibling rivalry forces me to always improve myself, and I believe this thesis gives me a momentary lead. 

Finally, I would like to thank my wife, Molly, for her love, support, advice and friendship. She is the only one who can bring me back to earth when I float off into space. 
% This line is required, but of course replace my initials with yours.
\\
\\
\\
\\
\\
\initials{PJM}