% It doesn't look like this is actaully used in our bibliography. We'll leave for the time being. 

\bibitem{Uslenghi1}
P. L. E. Uslenghi, “Exact Scattering by Isorefractive Bodies,”
IEEE Trans. Antennas Propagat., vol. 45, p. 1382, Sept. 1997.

\bibitem{Erricolo}
D. Erricolo, \emph{TBD Book Title}, Chapter 10, Date TBD 

\bibitem{Uslenghi2}
P. L. E. Uslenghi, “Exact Scattering from a Slotted Semielliptical Channel,”
IEEE Trans. TBD

\bibitem{Uslenghi3}
P. L. E. Uslenghi and R. E. Zich, “Radiation and Scattering from 
Isorefractive Bodies of Revolution,” IEEE Trans. Antennas Propagat., vol. 46, p. 1606, Nov. 1998. 

\bibitem{Ivanov}
V. I. Ivanov, \emph{Diffraction of Short Plane Waves on a Parabolic Cylinder}, 1961, Moscow

\bibitem{Bowman}
J. J. Bowman, T. B. A. Senior, and P. L. E. Uslenghi, Electromagnetic and Acoustic Scattering by Simple Shapes. Amsterdam, The Netherlands: North-Holland, 1969.

\bibitem{Askarpour}
A. N. Askarpour and P. L. E. Uslenghi, "Exact Radiation From Dipole Antennas on Oblate Spheroids Coated With Isorefractive and Anti-Isorefractive Layers," in IEEE Transactions on Antennas and Propagation, vol. 60, no. 11, pp. 5476-5479, Nov. 2012.

\bibitem{Erdelyi}
A. Erdelyi, W. Magnus, F. Oberhettinger, and F. G. Tricomi, Higher
Transcendental Functions. New York: McGraw-Hill, 1953.

\bibitem{Stutzman}
W. L. Stutzman and G. A. Thiele, Antenna Theory and Design, Third Edition, John Wiley and Sons, Inc., 2013

\bibitem{Beyersdorf}
P. Beyersdorf,  "Fresnel Equations,", powerpoint, 2006

